Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-08-04 STAT-paper-template/APA/fertile.Rnw
close #6

Several continuous integration code development tools external to R attempt to do this, providing a way to address different aspects of reproducibility with minimal code. For example, \pkg{Wercker}, a command line tool that leverages Docker, enables users to test whether their projects will successfully compile when run on a variety of operating systems without access to the user's local hard drive \cite{wercker}. \pkg{Travis CI} is integrated with GitHub and can be configured to do similar checks on projects hosted in repositories \cite{travis}. \pkg{Circle CI}, another popular continuous integration tool, can also be used to check R code \cite{circle}.

However, while these tools can be useful in some circumstances, they are generalized so as to be useful to the widest audience. As a result, their checks are not designed to be R-specific, which makes them sub-optimal for users looking to address reproducibility issues involving features specific to the R programming language, such as package installtion and seed setting.

>>>>

Several continuous integration code development tools external to \R attempt to do this, providing a way to address different aspects of reproducibility with minimal code. For example, \pkg{wercker}---a command line tool that leverages Docker---enables users to test whether their projects will successfully compile when run on a variety of operating systems without access to the user's local hard drive \cite{wercker}. GitHub Actions is integrated with GitHub and can be configured to do similar checks on projects hosted in repositories. \href{https://travis-ci.com}{Travis CI} and \href{https://circleci.com/product}{Circle CI} are popular continuous integration tools which can also be used to check \R code.

However, while these tools can be useful in some circumstances, they are generalized so as to be useful to the widest audience. As a result, their checks are not designed to be \R-specific, which makes them sub-optimal for users looking to address reproducibility issues involving features specific to the \R programming language, such as package installation and seed setting.
